\documentclass[a4paper,12pt]{article}
\setcounter{secnumdepth}{0}
\begin{document}

\begin{flushright}
   Steven Diviney \\
   14 Strand Road \\
   Sutton \\
   Dublin 13 \\
   0863807768 \\
   divines@tcd.ie \\* \vspace{10 mm}
\end{flushright}
\begin{flushleft}

{\LARGE\bf Steven Diviney} \\* \vspace{10mm}
\section{Objective:}    Dependable, energetic and hard working student studying computer science, looking for internship opportunities in a reputed organisation.
\section{Experience:}
\subsection{GeSCI} Co-developed open-source software to assist with the calculation of ICT costs across a country. Software is now deployed in several Ministry's of Education across Africa, distributed freely from GeSCIs website. 
\subsection{Freelance Graphic Design} Notable aspects include:\\
Consulting with clients in order to assess their requirements.\\
Creating of drafts based on clients requirements.\\
Refining draft into final copy.\\
\subsection{Secretarial Duties} Notable aspects include: \\
Receival and redirection of messages.\\
Co-ordinating orders from management to employees.\\
Taking in invoices and registering them in database applications.\\
\section{Education}
\subsection{Sutton Park: 2002-2008}
Attended Sutton Park Secondary School from 2002-2008, obtained Leaving Certificate in August 2008, results available upon request. In addition I obtained a GCSE in ICT in 2006, also available upon request. 
\subsection{Trinity College, Dublin: 2008-Present}Currently studying as a Junior Sophister in Computer Science.\\
Presently perusing B.A. mod in Computer Science. Expected to graduate in summer 2012\\
Junior Freshman achieved II.I\\
Senior freshman achieved II.II\\
\section{Skills}GNU/Linux (primary Debian), Windows 7,  Vista, XP \\ 
Good level of experience programming in C/C++, Java and Bash. In addition I have some experience / working knowledge of Python, VHDL, HTML, CSS, PHP, Eiffel and Prolog. 
\section{Interests}My interests include but are not limited to computer programming, Unix based operating systems, graphic design, photography and embedded systems . I also have a small amount of experience with web-design. An example of some of my work can be found at netsoc.tcd.ie/~divines
\section{References}Can be provided upon request



\end{document}
