% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Steven Diviney} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{Steven Diviney}
\address{14 Strand Road\\
Sutton\\
Dublin 13\\
086 3807768\\
divoapple@gmail.com}



\begin{resume}
\vspace{0.1in}
\moveleft.5\sectionwidth\centerline{Objective: Fourth year Computer Science student looking for internship opportunities in a reputed organization.}  

\section{Experience} 
\vspace{0.1in}
     
    {\bf IBM Ireland, 2011 }Summer internship for 3 months at IBM Ireland as part of their Extreme Blue internship program. Worked on a web application as part of a team of four. The project was voted second out of over twenty at the end of the internship. As well as creating the application we were required to give a weekly update presentation to our managers and co-workers.
 
    {\bf GeSCI, 2010} Co-developed open-source software to assist with the calculation of ICT costs across a country. The software is now deployed in several Ministry's of Education across Africa, distributed freely from GeSCIs website. I was responsible for creating the front-end.

    {\bf Dangerous Goods Safety Advisor, 2010 - Present} I am responsible for ensuring that two organizations adhere to the requirements set out by the European Agreement concerning the International Carriage of Dangerous Goods by Road. Notable aspects include inspection of sites to ensure regulations are being adhered too, consultation with the organizations if regulations are not being met and the submission of an annual report to the HSA. 
 
    {\bf Freelance Graphic Design} Notable aspects include; Consulting with clients in order to assess their requirements. Creating of drafts based on clients requirements. Refining draft into final copy.

 
    {\bf Secretarial Duties} Notable aspects include: Receival and redirection of messages. Co-ordinating orders from management to employees. Taking in invoices and registering them in database applications.

 
   
 

\section{EDUCATION}
\vspace{0.1in} 
 
    Trinity College, Dublin, BA(mod),\\ 
    Computer Science, 2008 - Present\\
    Junior Freshman achieved II.I\\
    Senior Freshman achieved II.II\\
    Junior Sophister achieved II.I \\
 
    Sutton Park, Sutton, Dublin, 2002- 2008,\\
    Leaving certificate obtained in 2008, available on request.\\
    GCSE in ICT obtained in 2006, available on request.\\
    
     
\section{SKILLS} 
\vspace{0.1in}
 {\bf Operating Systems}
    \begin{itemize} % Use \item[] to prevent a bullet from appearing
      \item[] GNU/Linux, primarily Debian based, very good working and theoretical knowledge.\\
        Windows 7, Vista, XP, very good working knowledge.
      \end{itemize}
{\bf Programming} 
       \begin{itemize}
        \item[] Very good level of experience programming in C/C++, Java, Bash, Python and Javascript.\\
        I have a good knowledge of OOP concepts and design patterns as well as functional, imperative and declarative programming paradigms.  
        In addition I have a good working knowledge of Haskell, Prolog, PHP, SQL (Oracle DBMS, IBM DB2 and MySQL), VHDL, Eiffel, CSS, HTML and C\#.
    \end{itemize}

  {\bf Design} 
        \begin{itemize}
        \item[] I have a good knowledge of graphic design concepts and the technical knowledge on how to apply them. This applies to both graphic and user interface design.
       \end{itemize}

   {\bf  Electronics} 
        \begin{itemize}
        \item[]  I have some experience working with embedded electronics, primarily the Atmel AVR series of chips.
       \end{itemize} 

 

 

\end{resume}
\end{document}






























